Preregistration

### 2021-04-15 preregistration.Rmd
containerise preregistration/simulation

---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
params:
  nsim: 1000
  nmin: 100
  nmax: 10000
  nstep: 100
  seed: 1234
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)

library(tidyverse)
library(lavaan)
library(furrr)
library(slider)
library(patchwork)
source(here::here("R", "simulation.R"))
# if you have access to a hpc envir specify this in R/hpc.R
# if not we use local multicore
# to speed up consider reduce nsim; increase nstep in ↑YAML↑

@@

setup <- expand_grid(n_obs = n_obs,
                     truth = model_truth,
                     same = model_same,
                     differ = model_differ,
                     mod_load = c(3),
                     mod_int = c(3),
                     extract_fns = list(extract_fns),
                     group.equal = list(c("loadings", "intercepts")),
                     auto.fix.first = FALSE)
to_export <- ls_funs() %>% map(get)
to_export <- c(list(setup = setup), to_export)
RNGkind("L'Ecuyer-CMRG")
set.seed(params$seed)
res_raw %<-% generate_data_setup(n_sim,
                setup,
                furrr_options(
                  globals = to_export,
                  seed = params$seed,
                  packages = c("furrr", "lavaan", "tidyverse")
                ))
```

```{r write-out, error=TRUE, include=FALSE}
write_rds(res_raw, here::here("res_raw.rds"))
```

@@

>>>>

---
title: "Preregistration"
author: "Aaron Peikert"
date: "4/12/2021"
output: html_document
params:
  nsim: 1000
  nmin: 100
  nmax: 1000
  nstep: 100
  seed: 1234
repro:
  packages:
    - tidyverse
    - here
    - lavaan
    - furrr
    - future.batchtools
    - slider
    - patchwork
    - svglite
  scripts:
    - R/simulation.R
---

```{r setup, include=FALSE}
library(tidyverse)
library(lavaan)
library(furrr)
library(slider)
library(patchwork)
source(here::here("R", "simulation.R"))
# if you have access to a hpc envir specify this in R/hpc.R
# if not we use local multicore
# to speed up consider reduce nsim; increase nstep in ↑YAML↑

@@

setup <- expand_grid(n_obs = n_obs,
                     truth = model_truth,
                     same = model_same,
                     differ = model_differ,
                     mod_load = c(3),
                     mod_int = c(3),
                     extract_fns = list(extract_fns),
                     group.equal = list(c("loadings", "intercepts")),
                     auto.fix.first = FALSE)
to_export <- ls_funs() %>% map(get)
to_export <- c(list(setup = setup), to_export)
RNGkind("L'Ecuyer-CMRG")
set.seed(params$seed)
seed <- params$seed
res_raw %<-% generate_data_setup(n_sim,
                setup,
                furrr_options(
                  globals = to_export,
                  seed = seed,
                  packages = c("furrr", "lavaan", "tidyverse")
                ))
```

```{r write-out, error=TRUE, include=FALSE}
invisible(res_raw)
write_rds(res_raw, here::here("res_raw.rds"))
```

@@

# Session Info

```{r}
if(fs::file_exists(hpc_config)){
  list(local = sessioninfo::session_info(),
     login_node = value(future(sessioninfo::session_info())),
     worker = value(future(value(future(sessioninfo::session_info())))))
} else {
  sessioninfo::session_info()
}
```
